Visualizing probability distributions across bivariate cyclic temporal granularities

### 2021-04-22 main.Rmd
had to remove the definition line in the yaml because it was duplicated in one of the packages used
typo in Dfinition 6

\begin{definition}\label{def:periodic}
A granularity $G$ is \textbf{periodic} with respect to a finite granularity $H$ if:
(1) $G \trianglelefteq H$; and
(2) there exist $R$, $P \in \mathbb{Z}_+$, where $R$ is less than the number of granules of $H$, such that for all $i \in \mathbb{Z_\geq 0}$, if $H(i) = \bigcup_{j \in S}G(j)$ and $H (i + R) \neq \phi$ then $H (i + R) = \bigcup_{j \in S} G(j + P)$.
\end{definition}

@@

Granularities can also be periodic with respect to other granularities, except for a finite number of periods where they behave in an anomalous way; these are called **quasi-periodic** relationships [@Bettini2000-vy]. In a Gregorian calendar with leap years, day groups quasi-periodically into month with the exceptions of the time domain corresponding to $29^{\text{th}}$ February of any year.

>>>>

\begin{definition}\label{def:periodic}
A granularity $G$ is \textbf{periodic} with respect to a finite granularity $H$ if:
(1) $G \trianglelefteq H$; and
(2) there exist $R$, $P \in \mathbb{Z}_+$, where $R$ is less than the number of granules of $H$, such that for all $i \in \mathbb{Z}_{\geq 0}$, if $H(i) = \bigcup_{j \in S}G(j)$ and $H (i + R) \neq \phi$ then $H (i + R) = \bigcup_{j \in S} G(j + P)$.
\end{definition}

@@

Granularities can also be periodic with respect to other granularities, "except for a finite number of spans of
time where they behave in an anomalous way"; these are called **quasi-periodic** relationships [@Bettini2000-vy]. In a Gregorian calendar with leap years, day groups quasi-periodically into month with the exceptions of the time domain corresponding to $29^{\text{th}}$ February of any year.
